BivData Setup

### 2020-02-21 doc/Results.rmd
small changes

@@

When the t.tests were performed within each strain, all but KAZ show (p-value = 0.3), significant sex differences in the normalized IFD measures
MSM
SKIVE
PWD
MSM
LEW
G
WSB

@@

>>>>

DO THE HIGH QUALITY

@@

When the t.tests were performed within each strain, all but KAZ show (p-value = 0.3), significant sex differences in the normalized IFD measures
MSM   `r `
SKIVE  `r `
PWD  `r `
MSM  `r `
LEW  `r `
G  `r `
WSB  `r `

@@

**THE male female pattern** female close to 50% -- which fits with uniform rec landscape / weak interference

### 2020-02-21 src/BivData_Setup.Rmd
small changes

cell.level.BivData_table <- add_mouse(cell.level.BivData_table)
cell.level.BivData_table <- add_strain(cell.level.BivData_table)
cell.level.BivData_table <- add_category(cell.level.BivData_table)

>>>>

cell.level.BivData_table <- add_mouse(cell.level.BivData_table)
cell.level.BivData_table <- add_sex(cell.level.BivData_table)
cell.level.BivData_table <- add_strain(cell.level.BivData_table)
cell.level.BivData_table <- add_category(cell.level.BivData_table)
